### 2017-02-28 2017mergingmerges/section/02-Processes.tex
I am the king of colours

%%% AR: would like to highlight which machine is performing the current instruction, eg bolding "A0" when it's group moving from A0 to A1
\begin{figure}
\begin{code}
process
{ ins:    { sIn1,  sIn2 }
, outs:   { sOut1, sOut2 }
, heap:   { f = T, l = 0, v = 0, x1 = 0, x2 = 0, b1 = 0}
, label:  F0
\end{code}

\definecolor{groupc}{HTML}{308030}
\definecolor{mergec}{HTML}{800000}
\definecolor{sharec}{HTML}{000080}

@@

\caption{Fusion of group and merge}
\label{fig:Process:Fused}
\end{figure}

>>>>

%%% AR: would like to highlight which machine is performing the current instruction, eg bolding "A0" when it's group moving from A0 to A1
\begin{figure}
\definecolor{groupc}{HTML}{308030}
\definecolor{mergec}{HTML}{800000}
\definecolor{sharec}{HTML}{000080}

\newcommand\tctt[2]{\textcolor{#1}{\tt{#2}}}
\begin{alltt}
process
\string{ ins:    \string{ \tctt{sharec}{sIn1},  \tctt{mergec}{sIn2} \string}
, outs:   \string{ \tctt{groupc}{sOut1}, \tctt{mergec}{sOut2} \string}
, heap:   \string{ \tctt{groupc}{f = T, l = 0, v = 0}, \tctt{mergec}{x1 = 0, x2 = 0}, \tctt{sharec}{b1 = 0} \string}
, label:  \tctt{sharec}{F0}
\end{alltt}

@@

\caption{Fusion of \textcolor{groupc}{group} and \textcolor{mergec}{merge}, along with \textcolor{sharec}{shared} instructions}
\label{fig:Process:Fused}
\end{figure}
